MSHS COVID-19 Vaccinations

### 2021-09-30 Amb_Sched_Tracking.Rmd
Add a column with total for arrived and scheduled appointments.

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS")

@@

kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
        align = "c", digits = 0,
        # caption = paste("Dose 3 Schedule"),
      col.names = col_names_table) %>%
    kable_styling(bootstrap_options = "hover", position = "center",
                  font_size = 11, full_width = FALSE) %>%
    column_spec(column = c(1,
                           ncol(dose3_sch_next_2wks_cast)),
                border_right = "thin solid lightgray") %>%
    add_header_above(c(" " = 1,
                       "Arrived Visits" = arr_cols,
                       "Scheduled Visits" = sch_cols),
                     background = c("",
                                    sinai_colors[1],
                                    sinai_colors[3]),
                     line = FALSE,
                     color = "white") %>%
    row_spec(row = nrow(dose3_sch_next_2wks_cast),
             bold = TRUE,
             italic = TRUE,
             hline_after = TRUE) %>%
    scroll_box(width = "800px")

>>>>

dose3_sch_next_2wks_cast <- dose3_sch_next_2wks_cast %>%
  adorn_totals(where = "row",
               na.rm = TRUE,
               name = "MSHS") %>%
  adorn_totals(where = "col",
               na.rm = TRUE,
               name = "Total")

@@

kable_dose3_sch <- kable(dose3_sch_next_2wks_cast, format = "html", escape = FALSE,
        align = "c", digits = 0,
        # caption = paste("Dose 3 Schedule"),
      col.names = col_names_table) %>%
  kable_styling(bootstrap_options = "hover",
                position = "center",
                font_size = 11,
                full_width = FALSE) %>%
  column_spec(column = c(1,
                         ncol(dose3_sch_next_2wks_cast) - 1,
                         ncol(dose3_sch_next_2wks_cast)),
              border_right = "thin solid lightgray") %>%
  add_header_above(c(" " = 1,
                     "Arrived Visits" = arr_cols,
                     "Scheduled Visits" = sch_cols,
                     " " = 1),
                   background = c("",
                                  sinai_colors[1],
                                  sinai_colors[3],
                                  ""),
                   line = FALSE,
                   color = "white") %>%
  row_spec(row = nrow(dose3_sch_next_2wks_cast),
           bold = TRUE,
           italic = TRUE,
           hline_after = TRUE) %>%
  column_spec(column = ncol(dose3_sch_next_2wks_cast),
           bold = TRUE,
           italic = TRUE) %>%
  scroll_box(width = "800px")
